## Appendix

```{r}
library(survival)
library(KMsurv)
library(ggplot2)
library(ggpubr)
library(survminer)
library(muhaz)
library(plyr)
library(plotly)
library(ggthemes)
```

```{r}
# Loading in data
data(std)
# Checking for NA Values in data set 
any(is.na(std))
factor.cols <-
  c(
    "race",
    # Race (W=white, B=black)
    "marital",
    # Marital status (D=divorced / separated, M=married, S=single)
    "iinfct",
    # Initial infection (1= gonorrhea, 2=chlamydia, 3=both)
    "os12m",
    # Oral sex within 12 months (1=yes, 0=no)
    "os30d",
    # Oral sex within 30 days (1=yes, 0=no)
    "rs12m",
    # Rectal sex within 12 months (1=yes, 0=no)
    "rs30d",
    # Rectal sex within 30 days (1=yes, 0=no)
    "abdpain",
    # Presence of abdominal pain (1=yes, 0=no)
    "discharge",
    # Sign of discharge (1=yes, 0=no)
    "dysuria",
    # Sign of dysuria (1=yes, 0=no)
    "condom",
    # Condom use (1=always, 2=sometime, 3=never)
    "itch",
    # Sign of itch (1=yes, 0=no)
    "lesion",
    # Sign of lesion (1=yes, 0=no)
    "rash",
    # Sign of rash (1=yes, 0=no)
    "lymph",
    # Sign of lymph (1=yes, 0=no)
    "vagina",
    # Involvement vagina at exam (1=yes, 0=no)
    "dchexam",
    # Discharge at exam (1=yes, 0=no)
    "abnode" # Abnormal node at exam (1=yes, 0=no)
  )
std[factor.cols] <- lapply(std[factor.cols], as.factor)
#lapply(std, class)
std$race <-
  mapvalues(std$race,
            from = c("W", "B"),
            to = c("White", "Black"))
std$marital <-
  mapvalues(
    std$marital,
    from = c("D", "M", "S"),
    to = c("Divorced/Separated", "Married", "Single")
  )
std$iinfct <-
  mapvalues(
    std$iinfct,
    from = c("1", "2", "3"),
    to = c("gonorrhea", "chlamydia", "both")
  )
std$condom <-
  mapvalues(
    std$condom,
    from = c("1", "2", "3"),
    to = c("always", "sometime", "never")
  )

# Building the Survival Object 
infect <- std$iinfct
surv_object <- Surv(time = std$time, event = std$rinfct)
```

### Exploratory Data Analysis

Take a look at correlation between symptoms and different infection types.

Is it more common for one type of infection based on type of sex (oral/anal).

```{r}
fig1 <-
  plot_ly(
    data = data.frame(table(std$iinfct)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig1 <-
  fig1 %>% layout(
    title = "Percentage of Infection Type",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig1
fig2 <-
  plot_ly(
    data = data.frame(table(std$npartner)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig2 <-
  fig2 %>% layout(
    title = "Number of Partners",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig2
```

### Kaplan-Meier Curves 
```{r}
KMobj <- survfit(surv_object ~ iinfct, data = std)
KMplot <- ggsurvplot(KMobj) + labs(title = "Kaplan-Meier Curves for Initial Infection Type") 
ggplotly(KMplot[[1]])
```

### Kaplan-Meier Curves differences by actual numbers 

```{r}
print(survdiff(surv_object ~ iinfct, data = std))
```


### Plot the cumulative hazards vs. time and the complimentary log-log survival vs. log time.

```{r}
{plot(survfit(surv_object ~ iinfct, data = std),col=4:6,lwd=1,fun="cumhaz")
title("Cumulative Hazard for intital infection")
legend("topleft",c("gonorrhea","chlamydia","both"),col=4:6,lwd=1)}
```

```{r}
NAcurves <- survfit(surv_object ~ iinfct, data = std,type="fleming-harrington")
{plot(NAcurves,col=1:2,lwd=2,fun="cloglog", ylab = "ln[H(t)]", xlab = "ln(t)")
title("Complimentary log-log survival vs. log time")
legend("bottomright",c("gonorrhea","chlamydia","both"),col=1:2,lwd=2)}
```


# Add hazard ratio plot.
 
 
```{r}
cox <- coxph(surv_object ~ iinfct, data = std)
summary(cox)
hodg.zph <- cox.zph(cox)
plot(hodg.zph, main = "Schoenfeld Residuals for Initial Infection Type")
test.ph <- cox.zph(cox)
test.ph
```

P-value here is large, so we do not have a violation of proportional hazards.

```{r}
cox1 <- coxph(surv_object~iinfct+marital+race+os12m+os30d+rs12m+rs30d+abdpain+ discharge+dysuria+condom+itch+lesion+rash+lymph+vagina+dchexam+abnode+age+yschool+npartner, data = std)
summary(cox1)
drop1(cox1,test = "Chisq")
```

Drop test indicates that condom may also be significant.

```{r}
cox2<- coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
summary(cox2)
cox3<- coxph(surv_object ~ iinfct+vagina+dchexam+yschool, data = std)
summary(cox3)

AIC(cox2)
AIC(cox3)

# AIC indicates that the model with condom is a better fit.

std$condom <-
  mapvalues(
    std$condom,
    from = c("always", "sometime", "never"),
    to = c("use", "use", "never")
  )

cox4<- coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
summary(cox4)
drop1(cox4)

AIC(cox4)

# AIC is also now lower, so this will be our model.

```


## NEED TO CHANGE EVERYTHING FROM HERE DOWN.

```{r}
mres <- residuals(cox2, type = "martingale")
yearslowess <- lowess(std$yschool,mres)
{plot(std$yschool,mres,xlab="Years at School",ylab="Martingale Residuals")
lines(yearslowess)
title("Martingale Residuals vs. Years of School")}
```

```{r}
mres1 <- residuals(cox2, type = "martingale")
agelowess <- lowess(std$age,mres)
{plot(std$age,mres1,xlab="age",ylab="Martingale Residuals")
lines(agelowess)
title("Martingale Residuals vs. Age")}
```

```{r}
mres2 <- residuals(cox2, type = "martingale")
nlowess <- lowess(std$npartner,mres)
{plot(std$npartner,mres2,xlab="npartner",ylab="Martingale Residuals")
lines(nlowess)
title("Martingale Residuals vs. Number of Partners")}
```


```{r}
KMcurves1 <- survfit(surv_object ~ dchexam, data = std)
plot(KMcurves1, col = 1:2, main = "KM Curves for Discharge at Exam")
```





# Need to edit below now that we might be keeping condom.

### (4) Run the usual suite of model checking methods and report any interesting findings. Possibly alter the model as a result.
```{r}
test.ph <- cox.zph(cox2)
test.ph
```
```{r}
plot(test.ph[1], main = "Schoenfeld Residuals for differernt initial infection types")
```

```{r}
plot(test.ph[2], main = "Schoenfeld Residuals for whether vagina or not")
```

```{r}
plot(test.ph[3], main = "Schoenfeld Residuals for whether discharge or not at exam")
```

```{r}
plot(test.ph[4], main = "Schoenfeld Residuals for year at school")
```


```{r}
correlations <- apply(X = test.ph$y, MARGIN = 2, FUN = function(x) {cor.test(x, test.ph$x, method = "spearman")})
correlations
```

```{r}
residuals <- residuals(cox2,type="martingale")

add.cs <- as.numeric(std$rinfct)-residuals


surv.csr <- survfit(Surv(add.cs,as.numeric(std$rinfct))~1,type="fleming-harrington")

{plot(surv.csr,fun="cumhaz",xlab="Cox-snell residuals",ylab="Cumulative Hazard")
abline(0,1)
title("Cumulative Hazard of Cox-Snell Residuals")}
```

```{r}
b.mart <- residuals(cox2,type="martingale")
b.dev <- residuals(cox2,type="deviance")
b.dfb <- residuals(cox2,type="dfbeta")

b.preds <- predict(cox2)
{plot(b.preds,b.mart,xlab="Linear Predictor",
     ylab="Martingale Residual", ylim = c(-2,2), pch = 19, cex = 0.5)
text(b.preds,b.mart)
title("Martingale Residuals vs. Linear Predictor")}
```

```{r}
{plot(b.preds,b.dev,xlab="Linear Predictor",ylab="Deviance Residual", 
     ylim = c(-3,3), pch = 19, cex = 0.5)
title("Deviance Residuals vs. Linear Predictor")
text(b.preds,b.dev)}
```

```{r}
{plot(b.dfb[,1],xlab="Observation Number",ylab="dfbeta for clinics", 
     ylim=c(-.2,.2), pch = 19, cex = 0.5)
text(b.dfb[,1])
title("dfbeta Values by Observation Number for initial infection")}
```

```{r}
{plot(b.dfb[,2],xlab="Observation Order",ylab="dfbeta for prison", pch = 19, cex = 0.5)
text(b.dfb[,2]+.04)
title("dfbeta Values by Observation Order for vigina or not")}
```

```{r}
{plot(b.dfb[,3],xlab="Observation Order",ylab="dfbeta for catergorized methadone", pch = 19, cex = 0.5)
text(b.dfb[,3]+.0005)
title("dfbeta Values by Observation Order for discharge or not")}
```


```{r}
{plot(b.dfb[,4],xlab="Observation Order",ylab="dfbeta for catergorized methadone", pch = 19, cex = 0.5)
text(b.dfb[,4]+.0005)
title("dfbeta Values by Observation Order for year at school")}
```





