---
title: "Analysis on Reinfection of Sexually Transmitted Diseases"
author: "Yichu Chen, Gu Gong, Kate Jones, Gianni Spiga"
date: '2022-11-29'
output:
  slidy_presentation: 
    highlight: "espresso"
    df_print: paged
  ioslides_presentation:
    widescreen: yes
---

# The Data 

- Sexually transmitted diseases are infections that are spread during vaginal, oral, or anal intercourse. Although sometimes undetected, STDs can cause serious health problems in individuals and lead to reproductive issues. Here, we examine two types of bacterial infections that can be easily treated once diagnosed. In order to understand the factors that influence the chance of reinfection and hopefully decrease the cases in high-risk populations, the following data was analyzed. Time to reinfection is studied for three different groups: those infected with gonorrhea, those infected with chlamydia, and those infected with both. We also analyze various predictors to see if they significantly influence the survival probability. 

- The predictors are as follows: 
  + race (white/black) 
  + marital status (divorced/separated, married, or single)
  + age
  + years of schooling
  + type of initial infection
  + number of partners
  + participating in oral sex in the last year and month
  + participating in rectal sex in the last year and month
  + presence of certain symptoms at time of initial infection
  + condom use
  + vaginal involvement at examination
  
- If we can understand the factors that lead to an increased risk of reinfection, we can utilize targeted preventive care and hopefully reduce the number of individuals who become infected.


```{r, echo = F, message = FALSE, warning=FALSE}
library(survival)
library(KMsurv)
library(ggplot2)
library(ggpubr)
library(survminer)
library(plotly)
library(muhaz)
library(ggthemes)
library(plyr)
library(tidyr)
```

```{r}
data(std)
std
```
- We will clean the data to make this more interpretable. 

```{r, echo=F, warning = F, message=FALSE}
# Loading in data
#data(std)
std0 = std
# Checking for NA Values in data set 
#any(is.na(std))

factor.cols <-
  c(
    "race",
    # Race (W=white, B=black)
    "marital",
    # Marital status (D=divorced / separated, M=married, S=single)
    "iinfct",
    # Initial infection (1= gonorrhea, 2=chlamydia, 3=both)
    "os12m",
    # Oral sex within 12 months (1=yes, 0=no)
    "os30d",
    # Oral sex within 30 days (1=yes, 0=no)
    "rs12m",
    # Rectal sex within 12 months (1=yes, 0=no)
    "rs30d",
    # Rectal sex within 30 days (1=yes, 0=no)
    "abdpain",
    # Presence of abdominal pain (1=yes, 0=no)
    "discharge",
    # Sign of discharge (1=yes, 0=no)
    "dysuria",
    # Sign of dysuria (1=yes, 0=no)
    "condom",
    # Condom use (1=always, 2=sometime, 3=never)
    "itch",
    # Sign of itch (1=yes, 0=no)
    "lesion",
    # Sign of lesion (1=yes, 0=no)
    "rash",
    # Sign of rash (1=yes, 0=no)
    "lymph",
    # Sign of lymph (1=yes, 0=no)
    "vagina",
    # Involvement vagina at exam (1=yes, 0=no)
    "dchexam",
    # Discharge at exam (1=yes, 0=no)
    "abnode" # Abnormal node at exam (1=yes, 0=no)
  )

std[factor.cols] <- lapply(std[factor.cols], as.factor)

#lapply(std, class)

std$race <-
  mapvalues(std$race,
            from = c("W", "B"),
            to = c("White", "Black"))
std$marital <-
  mapvalues(
    std$marital,
    from = c("D", "M", "S"),
    to = c("Divorced/Separated", "Married", "Single")
  )
std$iinfct <-
  mapvalues(
    std$iinfct,
    from = c("1", "2", "3"),
    to = c("gonorrhea", "chlamydia", "both")
  )
std$condom <-
  mapvalues(
    std$condom,
    from = c("1", "2", "3"),
    to = c("always", "sometime", "never")
  )
std$condom <-
  mapvalues(
    std$condom,
    from = c("always", "sometime", "never"),
    to = c("use", "use", "never")
  )


std
# Building the Survival Object 
#infect <- std$iinfct
surv_object <- Surv(time = std$time, event = std$rinfct)
```

# Exploratory Data Analysis

- Our first step is to visualize a few of the variables in our data: 

```{r, echo = F}
# ggplotly(
#   ggplot(std, aes(x = iinfct, fill = iinfct)) +
#     geom_bar(stat = "count", position = "dodge") +
#     # scale_y_continuous(labels = function(x) paste0(x*100, "%")) +
#     labs(title = "Number of Reinfection For Each Initial Infection Type",
#          x = "Initial Infection Type", y = "Count")
# )
```

- Below we create two pie charts. The first shows the percentages for each type of initial infection. The second shows the percentages for the number of partners each patient had. 
- Roughly 45% of the patients were initially infected by chlamydia, 16% of the patients were initially infected by gonorrhea; 39% of the patients were infected by both types of bacteria to start with. It looks like that infection by chlamydia was more commonly seen than infection by gonorrhea.
- About 70% of the patients reported to have 1 sex partner; 16.6% of them had 2 partners; 8% had no sex partner; it is very rare to have 3 or more sex partners; still, it is worth notice that one of the patients reported to have 19 sex partners.

```{r, echo = F}
fig1 <-
  plot_ly(
    data = data.frame(table(std$iinfct)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig1 <-
  fig1 %>% layout(
    title = "Percentage of Infection Type",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig1

fig2 <-
  plot_ly(
    data = data.frame(table(std$npartner)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig2 <-
  fig2 %>% layout(
    title = "Number of Partners",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig2
```
- We are also interested in the frequency of symptoms for each type of initial infection among those patients who were reinfected. Overall, discharge is the most common symptom for all three types of initial infection.
```{r, echo = F, message = F}
# From some_eda1 file
std0$iinfct <-
  mapvalues(
    std0$iinfct,
    from = c("1", "2", "3"),
    to = c("gonorrhea", "chlamydia", "both")
  )
# Symptom Percentages based on Initial Infection

symptoms <- c("itch","lesion","rash","lymph", "abdpain","discharge","dysuria")
ii_sub1 <- std0[which(std0$iinfct=="gonorrhea"),symptoms]
ii_sub2 <- std0[which(std0$iinfct=="chlamydia"),symptoms]
ii_sub3 <- std0[which(std0$iinfct=="both"),symptoms] 

ii_sub1 <- colSums((ii_sub1))/nrow(ii_sub1)
ii_sub2 <- colSums((ii_sub2))/nrow(ii_sub2)
ii_sub3 <- colSums((ii_sub3))/nrow(ii_sub3)

ii_sub1["infection"] = "gonorrhea"
ii_sub2["infection"] = "chlamydia"
ii_sub3["infection"] = "both"

ii_symptom <- as.data.frame(rbind(ii_sub1, ii_sub2, ii_sub3))

ii_symptom_long <- pivot_longer(ii_symptom, !infection, names_to="Symptom",values_to="percentage")
ii_symptom_long$percentage <- as.numeric(ii_symptom_long$percentage)

ggplotly(
  ggplot(ii_symptom_long, aes(
    x = infection, y = percentage, fill = Symptom
  )) +
    geom_col(position = "dodge") +
    scale_y_continuous(
      labels = function(x)
        paste0(x * 100, "%")
    ) +
    labs(title = "Distribution of Symptoms For Three Initial Infection Types",
         x = "Initial Infection Type", y = "Percentage") + theme_minimal()
)
```
- We can see that discharge is seen the most, regardless of infection type, while the least common symptom is symptoms involving the lymph nodes. 

```{r, echo = F, warning = F}
ggplotly(
  ggplot(data = std) +
    geom_boxplot(aes(
      x = as.factor(std$yschool),
      y = age,
      fill = as.factor(std$yschool)
    )) +
    labs(
      title = "Years of Education vs. Age",
      x = "Years of Schooling",
      y = "Age",
      fill = "Years"
    ) + scale_fill_brewer(palette = "BuPu")
)
```

```{r, warning = F, echo = F}
ggplotly(ggplot(data=std)+
  geom_boxplot(aes(x=as.factor(npartner), y=age, fill=as.factor(npartner)))+
  labs(title="Number of Partners vs. Age", x="Number of Partners", y="Age", fill = "Number of Partners") + scale_fill_brewer(palette="BuPu")
)
```

# Checking Proportionality 

- In order to build Cox model, we need to check that the data meets our proportional hazards assumptions. We will check this with *Kaplan-Meier Curves* and *Hazard Ratios*.

## Kaplan-Meier Curves 

- Before applying the Cox regression, we first test to ensure that the proportionality assumption was not violated for the base model that compares the three different types of infection. The Kaplan-Meier curves are plotted below, and it can be seen that at no point do the curves intersect. 
- The survdiff() function results indicate that there is a difference in survival time for the three categories of initial infection.

```{r, echo = F, warning = F}
KMobj <- survfit(surv_object ~ iinfct, data = std)
KMplot <-
  ggsurvplot(KMobj,
             palette = c("#daed64", "#6495ed", "#ed7864"),
             ggtheme = theme_minimal()) + labs(title = "Kaplan-Meier Curves for Initial Infection Type")
ggplotly(KMplot[[1]])
survdiff(surv_object ~ iinfct, data = std)
```

## Hazard Ratios 

- The Hazard Ratio plot indicates proportional hazards after some initial spiking in the curves before time = 100 days.

```{r, echo = F}
timevec <- 1:1500

#First hazard (Gonorrhea)
sf1 <- stepfun(KMobj[1]$time, c(1, KMobj[1]$surv))

#Second hazard (Chlamydia)
sf2 <- stepfun(KMobj[2]$time, c(1, KMobj[2]$surv))

#Third hazard (Both)
sf3 <- stepfun(KMobj[3]$time, c(1, KMobj[3]$surv))

#now we can find the cumulative hazards
cumhaz1 <- -log(sf1(timevec))
cumhaz2 <- -log(sf2(timevec))
cumhaz3 <- -log(sf3(timevec))

#Hazard Ratio
ggplotly(
  ggplot(ggtheme = theme_minimal()) + aes(x = timevec) + geom_line(aes(y = cumhaz1 / cumhaz2), col = "#daed64") + geom_line(aes(y = cumhaz3 / cumhaz1), col = "#6495ed") + geom_line(aes(y = cumhaz3 / cumhaz2), col = "#ed7864") +  labs(x = "Time", y = "Hazard Ratio", title = "Hazard Ratios for Three Initial Infections")
)
```
## Cumulative Hazards and CLogLog

- Further, the complementary log-log curves run parallel to each other after crossing once around time = 75 days.  

```{r, echo = F, warning = F}
# {plot(survfit(surv_object ~ iinfct, data = std),col=4:6,lwd=1,fun="cumhaz")
# title("Cumulative Hazard for intital infection")
# legend("topleft",c("gonorrhea","chlamydia","both"),col=4:6,lwd=1)}

# Interactive plot 
# Cumulative Hazard 
cumHazPlot <-
  ggsurvplot(
    KMobj,
    fun = "cumhaz",
    conf.int = FALSE,
    palette = c("#daed64", "#6495ed", "#ed7864"),
    ggtheme =theme_minimal()
  ) + ggtitle("Cumulative Hazard for Initial Infection Type")

ggplotly(cumHazPlot$plot)


# Complimentary Log-Log 
cLogLogPlot <-
  ggsurvplot(
    KMobj,
    fun = "cloglog",
    palette = c("#daed64", "#6495ed", "#ed7864"),
    ggtheme = theme_minimal()
  ) + ggtitle("Complimentary Log-Log for Initial Infection Type") 

ggplotly(cLogLogPlot[[1]])
```
- Once the initial Cox model was applied, the Schoenfeld residuals were plotted and there is no evidence of a non-random pattern that would suggest a violation of the assumptions.

```{r, echo = F}
cox <- coxph(surv_object ~ iinfct, data = std)
summary(cox)
hodg.zph <- cox.zph(cox)
# plot(hodg.zph, main = "Schoenfeld Residuals for Initial Infection Type")

#For initial infection
ggcoxzph(hodg.zph[1], se = FALSE, font.main = 12, ggtheme = theme_minimal(), point.col = "#6495ed")
```
- The cox.zph function was then applied to the model which resulted in a p-value of 0.24 reinforcing that the proportional hazards assumption is maintained. Therefore, we chose to apply the Cox model which is elaborated on the next slide.

# Model Selection

## The Full model

- We start with a full model that includes all covariates and then simplify the model after testing each covariate for significance. 

```{r, echo = T}
cox1 <-
  coxph(
    surv_object ~ iinfct + marital + race + os12m + os30d +
      rs12m + rs30d + abdpain + discharge + dysuria + condom + 
      itch + lesion + rash + lymph + vagina + dchexam + abnode +
      age + yschool + npartner,
    data = std
  )
summary(cox1)
```
- We then use the drop1() function to examine how the dropping of each variable influences the AIC of the model. 
```{r, echo = F}
#summary(cox1)
drop1(cox1, test = "Chisq")
```

- The summary of the cox model as well as the drop1() function indicated that initial infection type, condom use, vaginal involvement, discharge at exam, and years of school were significant.

## Simplifying the Model

- From here, the goal is to remove extraneous variables and include models that are statistically significant and lower the AIC of the model. 

- After creating a model with just these variables, condom use became less significant. However, no condom use is much more significant with a p-value of 0.14 versus a p-value of 0.80 for condom use sometimes. We create a model that drops the condom variable, but the AIC increases, suggesting that we should keep it. To see if recategorizing the values would lead to an increase in significance and decrease in AIC, we split condom use into two categories: never and use, where use includes individuals who sometimes use condoms and those who always use condoms. The new p-value for never using condoms was 0.009 and AIC decreased, so we kept the transformed variable in the model.

```{r}
cox.model = coxph(surv_object ~ iinfct+condom+vagina
                  +dchexam+yschool, data = std)
summary(cox.model)
```
- With our reduced model, we still have an overall highly significant model supported by the Liklihood Ratio Test, Wald test, and the Score test. 

- In the next slide, we will use residuals to address our considerations of stratification and transformation of quantitative variables. 

# Residuals




- We considered stratification, however, we found no signficant difference between a stratified and non-stratified model via the Cox Snell Residuals, which measure the overall fit of a Cox model. This coincides with our conclusion earlier that the proportional hazards assumption was not violated.

## Martingale 

### Transformation of Quantitative to a Categorical Variable
- We will create 
```{r, echo = F, warning = F}
cox.modelNoSchool <- coxph(surv_object ~ iinfct+condom+vagina+os30d+abdpain, data = std)
martNoSchool <- residuals(cox.modelNoSchool, type = "martingale")

# We plot martingale residuals to see if transformation is appropriate 
lowessOBJ <- as.data.frame(lowess(std$yschool, martNoSchool))

ggplotly(
  ggplot() + aes(std$yschool, martNoSchool) + geom_point() + 
    labs(x = "Years of School", y = "Martingale Residuals", title = "Martingale Residuals vs. Years of School") + 
    geom_line(data = lowessOBJ, aes(x = x, y = y), col = "#6495ed")
)

cat_yschool = cut(std$yschool,
                  c(-Inf, 8, 12, Inf),
                  labels = c("6-8", "9-12", "above 12"))
std['cat_yschool'] = cat_yschool

# re-level to use "9-12" as the reference group since it's survival curve is in between the other two groups

std$cat_yschool = relevel(std$cat_yschool, ref="9-12")
```
- Since our weighted least squares line is approximately straight, we decide to keep years of schooling a quantitative variable. 

```{r, echo = F}
# For the rest of the analysis.. 

############### THE FINAL MODEL #####################
# cox.model = coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
# summary(cox.model)
#####################################################

# Create residuals 
b.mart <- residuals(cox.model,type="martingale")
b.dev <- residuals(cox.model,type="deviance")
b.dfb <- residuals(cox.model,type="dfbeta")

b.preds <- predict(cox.model)
```

```{r, echo = F}
#Martingale vs Linear Predictor
ggplotly(
  ggplot() + aes(
    x = b.preds,
    y = b.mart,
    label = std$obs
  ) + geom_point() + labs(x = "Linear Predictor", y = "Martingale Residual", title = "Martingale Residuals vs Linear Predictor")
)
```

## Schoenfield

```{r, message = F, echo = F, warning = F}
#library(patchwork)
library(gridExtra)
test.ph <- cox.zph(cox.model)
test.ph

# #plot(test.ph[1], main = "Schoenfeld Residuals for differernt initial infection types")
# 
# #Condom use
# p1 <- ggcoxzph(test.ph[2], ggtheme =theme_minimal(),  se = FALSE, font.main = 12, point.col = "#ed7864")
# 
# #Vaginal use
# p2 <- ggcoxzph(test.ph[3], ggtheme =theme_minimal(),  se = FALSE, font.main = 12, point.col = "#ed7864")
# 
# #Discharge at exam use
# p3 <- ggcoxzph(test.ph[4], ggtheme =theme_minimal(),  se = FALSE, font.main = 12, point.col = "#ed7864")
# 
# # Years of schooling
# p4 <- ggcoxzph(test.ph[5], ggtheme =theme_minimal(),  se = FALSE, font.main = 12, point.col = "#ed7864")
# p1
# p2
# p3
# p4

ggplotly(ggcoxdiagnostics(cox.model, type = "schoenfeld"))
```


```{r}
# years of school  
figdfb1 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 6],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 4], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Years of School (Categorical)", title = "dfbeta Values for Years of School"),
  tooltip = "text"
)

# Discharge at Exam
figdfb2 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 5],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 5], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Discharge at Exam", title = "dfbeta Values for Discharge at Exam"),
  tooltip = "text"
)

# Vaginal Involvement
figdfb3 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 4],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 6], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Vaginal Involvement at Exam", title = "dfbeta Values for Vaginal Involvement at Exam"),
  tooltip = "text"
)


# Condom
figdfb4 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 3],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 6], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Condom", title = "dfbeta Values for Condom Usage"),
  tooltip = "text"
)


fig <- subplot(
  figdfb1,
  figdfb2,
  figdfb3,
  figdfb4,
  nrows = 2,
  shareX = TRUE,
  shareY = TRUE
) %>% layout(title = "dfBeta values for Years of Schooling, Discharge at Exam, Vaginal Involvement, \nand Condom Usage")

# Update title
annotations = list( 
  list( 
    x = 0.2,  
    y = 1.0,  
    text = "Years of Schooling",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.8,  
    y = 1,  
    text = "Discharge at Exam",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.2,  
    y = 0.475,  
    text = "Vaginal Involvement",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.8,  
    y = 0.475,  
    text = "Condom Usage",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ))

fig <- fig %>%layout(annotations = annotations) 
fig
```


## dfBeta 
```{r, echo = F}
# years of school  
figdfb1 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 6],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 4], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Years of School (Categorical)", title = "dfbeta Values for Years of School"),
  tooltip = "text"
)

# Discharge at Exam
figdfb2 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 5],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 5], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Discharge at Exam", title = "dfbeta Values for Discharge at Exam"),
  tooltip = "text"
)

# Vaginal Involvement
figdfb3 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 4],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 6], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Vaginal Involvement at Exam", title = "dfbeta Values for Vaginal Involvement at Exam"),
  tooltip = "text"
)


# Condom
figdfb4 <- ggplotly(
  ggplot() + aes(
    x = std$obs,
    y = b.dfb[, 3],
    text = paste("Obs:", std$obs, "\ndfBeta:", round(b.dfb[, 6], 4))
  ) + geom_point() + labs(x = "Observation Number", y = "Condom", title = "dfbeta Values for Condom Usage"),
  tooltip = "text"
)


fig <- subplot(
  figdfb1,
  figdfb2,
  figdfb3,
  figdfb4,
  nrows = 2,
  shareX = TRUE,
  shareY = TRUE
) %>% layout(title = "dfBeta values for Years of Schooling, Discharge at Exam, Vaginal Involvement, \nand Condom Usage")

# Update title
annotations = list( 
  list( 
    x = 0.2,  
    y = 1.0,  
    text = "Years of Schooling",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.8,  
    y = 1,  
    text = "Discharge at Exam",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.2,  
    y = 0.475,  
    text = "Vaginal Involvement",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.8,  
    y = 0.475,  
    text = "Condom Usage",  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ))

fig <- fig %>%layout(annotations = annotations) 
fig
```

## Cox-Snell
```{r, echo = F}
std.cs <- std$rinfct - b.mart

#Cumulative hazard 
surv.csr <- survfit(Surv(std.cs, std$rinfct) ~1, type = "fleming-harrington", data = std)

cumHazPlot <-
  ggsurvplot(
    surv.csr,
    fun = "cumhaz",
    conf.int = TRUE,
    palette = c("#581845"),
    ggtheme = theme_minimal()
  ) + ggtitle("Cumulative Hazard for Cox-Snell Residuals")

#ggplotly(cumHazPlot$plot + geom_abline())
cumHazPlot$plot + geom_abline()
```
# Outliers 

# In Conclusion 

## Our Best Model 

```{r, echo = F}
############### THE FINAL MODEL ####################
# cox.model = coxph(surv_object ~ iinfct+condom+vagina+yschool+os30d+abdpain+ condom + dchexam, data = std)
cox.model = coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
summary(cox.model)

drop1(cox.model)
#####################################################
```