## Appendix

```{r}
library(survival)
library(KMsurv)
library(ggplot2)
library(ggpubr)
library(survminer)
library(muhaz)
library(plyr)
library(plotly)
library(ggthemes)
library(MASS)
```

```{r}
# Loading in data
data(std)
# Checking for NA Values in data set 
any(is.na(std))



# add number of symptoms column
symptoms <- c("itch","lesion","rash","lymph", "abdpain","discharge","dysuria")
num_symptoms = rowSums(std[,symptoms])
num_symptoms <-
  mapvalues(
    num_symptoms,
    from = c(0,1,2,3,4,5),
    to = c("No Symptom","Has Symptom","Has Symptom","Has Symptom","Has Symptom","Has Symptom")
  )
std["num_symptoms"] = num_symptoms
std$num_symptoms = as.factor(std$num_symptoms)
std$num_symptoms = relevel(std$num_symptoms, ref="Has Symptom")




factor.cols <-
  c(
    "race",
    # Race (W=white, B=black)
    "marital",
    # Marital status (D=divorced / separated, M=married, S=single)
    "iinfct",
    # Initial infection (1= gonorrhea, 2=chlamydia, 3=both)
    "os12m",
    # Oral sex within 12 months (1=yes, 0=no)
    "os30d",
    # Oral sex within 30 days (1=yes, 0=no)
    "rs12m",
    # Rectal sex within 12 months (1=yes, 0=no)
    "rs30d",
    # Rectal sex within 30 days (1=yes, 0=no)
    "abdpain",
    # Presence of abdominal pain (1=yes, 0=no)
    "discharge",
    # Sign of discharge (1=yes, 0=no)
    "dysuria",
    # Sign of dysuria (1=yes, 0=no)
    "condom",
    # Condom use (1=always, 2=sometime, 3=never)
    "itch",
    # Sign of itch (1=yes, 0=no)
    "lesion",
    # Sign of lesion (1=yes, 0=no)
    "rash",
    # Sign of rash (1=yes, 0=no)
    "lymph",
    # Sign of lymph (1=yes, 0=no)
    "vagina",
    # Involvement vagina at exam (1=yes, 0=no)
    "dchexam",
    # Discharge at exam (1=yes, 0=no)
    "abnode" # Abnormal node at exam (1=yes, 0=no)
  )
std[factor.cols] <- lapply(std[factor.cols], as.factor)
#lapply(std, class)
std$race <-
  mapvalues(std$race,
            from = c("W", "B"),
            to = c("White", "Black"))
std$marital <-
  mapvalues(
    std$marital,
    from = c("D", "M", "S"),
    to = c("Divorced/Separated", "Married", "Single")
  )
std$iinfct <-
  mapvalues(
    std$iinfct,
    from = c("1", "2", "3"),
    to = c("gonorrhea", "chlamydia", "both")
  )
std$condom <-
  mapvalues(
    std$condom,
    from = c("1", "2", "3"),
    to = c("always", "sometime", "never")
  )

# Building the Survival Object 
infect <- std$iinfct
surv_object <- Surv(time = std$time, event = std$rinfct)
```

### Exploratory Data Analysis

Take a look at correlation between symptoms and different infection types.

Is it more common for one type of infection based on type of sex (oral/anal).

```{r}
fig1 <-
  plot_ly(
    data = data.frame(table(std$iinfct)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig1 <-
  fig1 %>% layout(
    title = "Percentage of Infection Type",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig1
fig2 <-
  plot_ly(
    data = data.frame(table(std$npartner)),
    labels = ~ Var1,
    values = ~ Freq,
    type = 'pie'
  )
fig2 <-
  fig2 %>% layout(
    title = "Number of Partners",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
fig2
```

### Kaplan-Meier Curves 
```{r}
KMobj <- survfit(surv_object ~ iinfct, data = std)
KMplot <- ggsurvplot(KMobj) + labs(title = "Kaplan-Meier Curves for Initial Infection Type") 
ggplotly(KMplot[[1]])
```

### Kaplan-Meier Curves differences by actual numbers 

```{r}
print(survdiff(surv_object ~ iinfct, data = std))
```


### Plot the cumulative hazards vs. time and the complimentary log-log survival vs. log time.

```{r}
{plot(survfit(surv_object ~ iinfct, data = std),col=4:6,lwd=1,fun="cumhaz")
title("Cumulative Hazard for intital infection")
legend("topleft",c("gonorrhea","chlamydia","both"),col=4:6,lwd=1)}
```

```{r}
NAcurves <- survfit(surv_object ~ iinfct, data = std,type="fleming-harrington")
{plot(NAcurves,col=1:3,lwd=2,fun="cloglog", ylab = "ln[H(t)]", xlab = "ln(t)")
title("Complimentary log-log survival vs. log time")
legend("bottomright",c("gonorrhea","chlamydia","both"),col=1:3,lwd=2)}
```


# Add hazard ratio plot.
 
 
```{r}
cox <- coxph(surv_object ~ iinfct, data = std)
summary(cox)
hodg.zph <- cox.zph(cox)
plot(hodg.zph, main = "Schoenfeld Residuals for Initial Infection Type")
test.ph <- cox.zph(cox)
test.ph
```

P-value here is large, so we do not have a violation of proportional hazards.

```{r}
cox1 <- coxph(surv_object~iinfct+marital+race+os12m+os30d+rs12m+rs30d+abdpain+ discharge+dysuria+condom+itch+lesion+rash+lymph+vagina+dchexam+abnode+age+yschool+npartner, data = std)
summary(cox1)
drop1(cox1,test = "Chisq")
```

Drop test indicates that condom may also be significant.  

```{r}
cox2<- coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
summary(cox2)
```
```{r}
cox3<- coxph(surv_object ~ iinfct+vagina+dchexam+yschool, data = std)
summary(cox3)
```
```{r}

AIC(cox2)

AIC(cox3)

# AIC indicates that the model with condom is a better fit.

std$condom <-
  mapvalues(
    std$condom,
    from = c("always", "sometime", "never"),
    to = c("use", "use", "never")
  )

cox4<- coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
summary(cox4)
drop1(cox4)

AIC(cox4)

# AIC is also now lower, so this will be our model.

```


## CODE BELOW: categorical version of yschool and cox5
```{r}
cat_yschool = cut(std$yschool, c(-Inf, 8, 12, Inf), labels = c("6-8","9-12","above 12"))
std['cat_yschool'] = cat_yschool

# re-level to use "8-12" as the reference group since it's survival curve is in between the other two groups

std$cat_yschool = relevel(std$cat_yschool, ref="9-12")
```

```{r}
# cox5 <- coxph(surv_object ~ iinfct+condom+vagina+dchexam+cat_yschool, data = std)
# 
# summary(cox5)
```


In cox6 the "discharge at exam" is dropped.

```{r}
# cox6 <- coxph(surv_object ~ iinfct+condom+vagina+cat_yschool, data = std)
# summary(cox6)
```

```{r}

# cox6.zph <- cox.zph(cox6)
# 
# plot(cox6.zph[1], main="Schoenfeld Residual for Initial Infectoion")
# 
# plot(cox6.zph[2], main="Schoenfeld Residual for Condom Use")
# 
# plot(cox6.zph[3], main="Schoenfeld Residual for Involvement of Vagina Examination")
# 
# plot(cox6.zph[4], main="Schoenfeld Residual for Schooling Years")

```


```{r}
KM_condom <- survfit(surv_object ~ condom, data = std)
KM_condom_plot <- ggsurvplot(KM_condom) + labs(title = "Kaplan-Meier Curves for Condom Use") 
KM_condom_plot
```

```{r}
############### THE FINAL MODEL #####################
cox.model = coxph(surv_object ~ iinfct+condom+vagina+dchexam+yschool, data = std)
drop1(cox.model, test="Chisq")
summary(cox.model)
#####################################################
```






```{r}
# Cox-Snell
cox.cs <- std$rinfct-residuals(cox.model, type="martingale")

# Cum. Hazard for cox-snell residual
cox.cs.surv <- Surv(cox.cs, std$rinfct)
cox.cs.fit <- survfit(cox.cs.surv~1,type="fleming-harrington")

plot(cox.cs.fit, fun="cumhaz", xlab="Cox-Snell Residuals", ylab="Cumulative Hazard")
abline(0,1, col=2, lwd=2, lty=2)
title("Cumulative Hazard of Cox-Snell Residuals")
```


## NEED TO CHANGE EVERYTHING FROM HERE DOWN.


### (4) Run the usual suite of model checking methods and report any interesting findings. Possibly alter the model as a result.
```{r}
test.ph <- cox.zph(cox.model)
test.ph
```

From the output results, the P values of the three covariates are all greater than 0.05, indicating that each variable satisfies the PH test, and the overall test P value of the model 0.4 is not statistically significant, so we believe that the model as a whole satisfies the PH test.

```{r}
plot(test.ph[1], main = "Schoenfeld Residuals for differernt initial infection types")
```

```{r}
plot(test.ph[2], main = "Schoenfeld Residuals for whether using condom or not")
```

```{r}
plot(test.ph[3], main = "Schoenfeld Residuals for whether vagina involvement or not")
```

```{r}
plot(test.ph[4], main = "Schoenfeld Residuals for wether discharge present or not at exam")
```

```{r}
plot(test.ph[5], main = "Schoenfeld Residuals for schooling years")
```

```{r}
# plot(test.ph[6], main = "Schoenfeld Residuals for whether having Presence of abdominal pain or not")
```


```{r}
# correlations <- apply(X = test.ph$y, MARGIN = 2, FUN = function(x) {cor.test(x, test.ph$x, method = "spearman")})
# correlations
```

And based on the correlation test, all variables induce no non-proportionality. That means we should include both variables in our model.

```{r} 

residuals <- residuals(cox.model,type="martingale")

add.cs <- as.numeric(std$rinfct)-residuals


surv.csr <- survfit(Surv(add.cs,as.numeric(std$rinfct))~1,type="fleming-harrington")

{plot(surv.csr,fun="cumhaz",xlab="Cox-snell residuals",ylab="Cumulative Hazard")
abline(0,1, col=2, lty=2, lwd=2)
title("Cumulative Hazard of Cox-Snell Residuals")}
```

```{r}
b.mart <- residuals(cox.model,type="martingale")
b.dev <- residuals(cox.model,type="deviance")
b.dfb <- residuals(cox.model,type="dfbeta")

b.preds <- predict(cox.model)
{plot(b.preds,b.mart,xlab="Linear Predictor",
     ylab="Martingale Residual", ylim = c(-2,2), pch = 19, cex = 0.5)
text(b.preds,b.mart)
title("Martingale Residuals vs. Linear Predictor")}
```

```{r}
{plot(b.preds,b.dev,xlab="Linear Predictor",ylab="Deviance Residual", 
     ylim = c(-4,4), pch = 19, cex = 0.5)
title("Deviance Residuals vs. Linear Predictor")
text(b.preds,b.dev)}
```

```{r}
{plot(b.dfb[,1],xlab="Observation Number",ylab="dfbeta for initial infection: chlamydia", 
     ylim=c(-.05,.05), pch = 19, cex = 0.5)
text(b.dfb[,1])
title("dfbeta Values by Observation Number for initial infection: chlamydia")}
```
```{r}
{plot(b.dfb[,2],xlab="Observation Number",ylab="dfbeta for initial infection: both", 
     ylim=c(-.04,.04), pch = 19, cex = 0.5)
text(b.dfb[,2])
title("dfbeta Values by Observation Number for initial infection: both")}
```

```{r}
{plot(b.dfb[,3],xlab="Observation Number",ylab="dfbeta for condom use", 
     ylim=c(-.02,.02), pch = 19, cex = 0.5)
text(b.dfb[,3])
title("dfbeta Values by Observation Number for condom use")}
```

```{r}
{plot(b.dfb[,4],xlab="Observation Order",ylab="dfbeta for involvement of vagina at exam", pch = 19, cex = 0.5, ylim = c(-0.06,0.06))
text(b.dfb[,4])
title("dfbeta Values by Observation Order for involvement of vagina at exam")}
```

```{r}
{plot(b.dfb[,5],xlab="Observation Order",ylab="dfbeta for discharge at exam", pch = 19, cex = 0.5, ylim=c(-0.08,0.08))
text(b.dfb[,5])
title("dfbeta Values by Observation Order for discharge at exam")}
```


```{r}
{plot(b.dfb[,6],xlab="Observation Order",ylab="dfbeta for years of school", pch = 19, cex = 0.5)
text(b.dfb[,6])
title("dfbeta Values by Observation Order for years of school")}
```

Based on the plot above, we can get that the outliers and influencial points in this data as below:

Martingale Residuals - 690

Deviance Residuals - No unusual point

initial infection: chlamydia Influence - 366, 211

initial infection: both Influence - 366

condom use or not Influence - 525

vagina involvement or not Influence - 831, 525, 11

discharge at exam Influence - 831, 859, 154

year at school Influence - 294, 525, 635, 743

The most important observations to examine seem to be  366, 525, 831, 743

```{r}
unusualpts <- c(366, 525, 831)
std[unusualpts,]
```

 * Patient 366: Had the worst type of initial infection (gonorrhea), used condom, and had relatively low schooling year (yschool=9), but was not reinfected after a long survival time (1439 days).    
 
 * Patient 525: Had the second worst type of initial infection (gonorrhea and chlamydia), with vagina involvement during exam and had low schooling year (yschool=8), but was not reinfected after a long survival time (1005 days).    
 
 * Patient 831: Had vagina involvement and no discharge at exam, but was not reinfected after a long survival time.   
 

<!-- Based on the result, we can see that all of them are not having oral sex last 30 days and have a relatively high education level based on their year at school, which are indicators for not having reinfection of std. -->

<!-- Person 66: gonorrhea, having Presence of abdominal pain, sometimes using condom -->

<!-- Person 366: gonorrhea, sometimes using condom -->

<!-- Person 93: both, having Presence of abdominal pain, always using condom -->

<!-- Person 699: both, always using condom -->

<!-- Person 41: 	chlamydia, always using condom, getting vagina involvement -->

<!-- Person 473: chlamydia, sometimes using condom, getting vagina involvement -->






